\bf Landslide: \\ Systematic Dynamic Race Detection in Kernel-space

### 2012-05-01 futurework.tex
minor changes in eval; futurework
buncha minor edits

Through our evaluation, we found many ways in which Landslide's user interface is lacking. These improvements would not be research developments, but would enhance the user experience in ways necessary for continuing work in the context of 15-410.\footnote{
Landslide is also missing functionality to automatically identify decision points when newly-forked threads become runnable but not immediately switched to. This was not necessary to find the \texttt{double\_thread\_fork} bug in POBBLES (Section~\ref{sec:eval-casestudy}) only because POBBLES automatically switched to the child thread immediately.}

@@

\subsection{Long-Running Testing Approaches}
\label{sec:future-shaping}

% TODO more
\subsubsection{Iterating Decision Sets}

>>>>

In Section~\ref{sec:eval-feedback}, we describe many ways in which Landslide's user interface is lacking. These improvements would not necessarily be research developments, but would enhance the user experience in ways necessary for continuing work in the context of 15-410.\footnote{
Landslide is also missing functionality to automatically identify decision points when newly-forked threads become runnable but not immediately switched to. This was not necessary to find the \texttt{double\_thread\_fork} bug in POBBLES (Section~\ref{sec:eval-casestudy}) only because POBBLES automatically switched to the child thread immediately.}

@@

\subsection{Long-Running Testing Approaches}
\label{sec:future-shaping}
% TODO more
\footnote{Garth coined the name ``shaping'' to refer to this testing approach.}
\subsubsection{Iterating Decision Sets}
